### 2014-03-15 Draft/background.tex
Revised Example, Related work, and background Section

Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
These advances in NLP have inspired researchers/practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in software engineering domain.

In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the software engineering specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.

@@

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches have demonstrated to achieve 97\%~\cite{SNLP1} accuracy in classifying POS tags for well written news articles.

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can achieve around 90\%~\cite{SNLP1} accuracy in classifying phrases and clauses over well written news articles.

@@

\textbf{Named Entity Recognition}~\cite{Finkel05ACL}. Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of information extraction that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc. These techniques help in associating predefined semantic meaning to a word or a group of words (phrase), thus facilitating semantic processing of named entities.

@@

\subsection{Software engineering specific NLP techniques}
\label{sub:SENLPback}

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned earlier, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has 8 different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

>>>>

Natural language is well suited for human communication, but converting natural language into unambiguous specifications that can be processed and understood by computers is difficult.
However, research advances~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03} have increased the accuracy of existing NLP techniques to annotate the grammatical structure of a sentence.
These advances in NLP have inspired researchers/ practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt/apply NLP techniques to solve problems in SE domain.

In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in previous work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.

@@

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches have demonstrated to be effective in classifying POS tags for well written news articles.

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can effectively classify phrases and clauses over well written news articles.

@@

%\textbf{Named Entity Recognition}~\cite{Finkel05ACL}. Also known as \textit{`entity identification'} and \textit{`entity extraction'}, these techniques are a subtask of information extraction that aims to classify words in a sentence into predefined categories such as names, quantities, expression of times, etc. These techniques help in associating predefined semantic meaning to a word or a group of words (phrase), thus facilitating semantic processing of named entities.

@@

\subsection{SE specific NLP techniques}
\label{sub:SENLPback}

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned previously, POS tagging works well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as a HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

### 2014-03-15 Draft/related.tex
Revised Example Section
Revised Example, Related work, and background Section

% "In contrast" switch up the wording a little bit

Our proposed approach touches a few research areas such as software verification,
NLP in software engineering, and document augmentation.
We next discuss the relevant work pertinent to our proposed approach in these areas.

%\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
Formal specifications such as code contracts have been an active area of research. Notably, code contracts that are the heart of design by contract approach have been very influential in the area of software engineering.
A significant amount of work has been done in automated inference of code contracts.
Existing approaches statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA}.
Furthermore, there are existing approaches that infer code-contract-like specifications
(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.

\subsection{NLP in Software Engineering}

NLP techniques are increasingly applied in the software engineering domain. 
NLP techniques have been shown to be useful in requirements engineering ~\cite{Sinha2009,Sinha2010,Gervasi2005},
usability of API documents~\cite{Dekel2009}, and other areas~\cite{Zhou2008,Little2009,pandita13:WHYPER}.
We next describe the most relevant approaches.

\textit{1. Access Control Policies}: Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works well on natural language texts in use cases, owing to well formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well formed.
Additionally, these approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

\textit{2. Resource Specifications}: Zhong et al.~\cite{zhong09SE} employ NLP and  Machine Learning (ML) techniques to infer resource specifications from API documents.
Their approach uses machine learning to automatically classify such rules.
In contrast, we attempt to parse sentences based on semantic templates and demonstrate that such an approach preforms reasonably well.
Furthermore, the performance of the proposed approach is dependent on the quality of the training sets used for ML.
In contrast, approach presented in this work is independent of such training set and thus can be easily extended to target respective problems addressed by them.

\textit{3. Code Comments}: Tan et al.~\cite{TanSOSP07} and Hwei-Tan et al.~\cite{tcomment} applied an NLP and ML  based approach on code comments/ Javadoc comments to detect mismatches between these comments and implementations. They rely on predefined rule templates targeted towards method invocation and lock related comments, thus limiting their scope both in terms of application area as well as language used in the comments. In contrast, approach presented in this report relies on generic natural language based templates thus relaxing the restriction on the style of the language used to describe specifications.

\textit{4. API Description}: Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents. In contrast this approach deals with the temporal constraints. The approach presented here is a significant extension to the infrastructure used in the previous work as documented in Section~\ref{sec:approach}.

\subsection{Augmented Documentation}

Another related field has been that of improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment}. We next describe most relevant approaches. Dekel et al.~\cite{Dekel2009}, were the first to create a tool namely eMoose, an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives (way of marking the specification sentences) in the default API documentation. These directives are highlighted whenever they are displayed in the eclipse environment. Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009}, thus allowing tool based verification. However, a developer has to manually annotate such directives. In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.

>>>>

Our proposed approach touches a few research areas such as software verification, NLP in Software Engineering (SE), and document augmentation.
We next discuss the relevant work pertinent to our proposed approach in these areas.

%\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
\textbf{Formal Specification}:
Contracts have become an a well-known mechanism for formally specifying functional behavior of the software. 
Contracts specify the behavior in terms of conditions that must hold before/after and during the execution of the method.
A significant amount of work has been done in automated inference of contracts.
Existing approaches use program analysis~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}
as means to automatically infer contracts.
However, recent studies~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA} demonstrate that a combination of developer-written and automatically extracted
contracts is the most effective approach for formally specifying the constraints on an API.
Since  our approach infers temporal constraint from API documents, we believe our approach can work in conjunction with existing approaches
to infer a compressive set of specifications.

Furthermore, another set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries. In contrast, the approach presented in this report infers specifications from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.

\textbf{NLP in SE}:
NLP techniques are being increasingly applied in the SE domain. 
Tan et al.~\cite{TanSOSP07} were the first to apply Machine Learning (ML) and NLP on code comments to detect mismatches between the comments and the implementation.
They rely on predefined rule templates targeted towards threading and lock related comments, thus limiting their scope both in terms of application area as well as language used in the comments.
Furthermore, the constraints inferred by their approach are the restrictions imposed by the developer on the client code.
In comparison, the temporal constraints inferred by our approach are the restriction imposed by the API library being used by the client code.
Furthermore, approach presented in this report relies on generic natural language based templates thus relaxing the restriction on the style of the language used to describe specifications.

Zhong et al.~\cite{zhong09SE} leverage machine learning and type information to infer constraints on resources based on phases of resource usage: creating, manipulating, and releasing.
However, temporal constraints are not limited to resource usage thus 
Furthermore, the specifications inferred by their approach infers implicit specifications across multiple method descriptions,
whereas the temporal constraints inferred by our approach infers explicit ordering information described in individual method descriptions.
Furthermore, the performance of their approach is dependent on the quality of the training sets used for ML.
In contrast, approach presented in this report is independent of such training set and thus can be easily extended to target respective problems addressed by them.

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language texts in use cases, owing to well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, these approaches do not deal with programming keywords or identifiers, which are often mixed within the method descriptions in API documents.

Most closely related work to the approach presented here is Pandita et al.~\cite{pandita12:inferring} work on inferring parameter constraints from method descriptions in the API documents.
Our proposed approach differs from the previous approach as follows.
Our proposed approach addresses the problem of inferring temporal constraint, whereas the previous approach infers parameter constraints.
Our proposed approach is a significant extension to the infrastructure used in the previous work in following areas.
First, the proposed approach introduces hybrid shallow parsing that relies both on POS tags as well as Stanford-typed dependencies to construct intermediate representation.
Second, the proposed approach introduces a new heuristics namely frequent phrase reduction to deal with the domain specific and ill-formed sentences in API documents.
Finally, the proposed approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

\textbf{Augmented Documentation}:
Improving the documentation related to an software API~\cite{Dekel2009,tan2011acomment} is another related field of research.
Dekel and Herbsleb~\cite{Dekel2009}, were the first to create a tool namely eMoose,
an Eclipse~\footnote{\url{http://www.eclipse.org/}} based plug-in that allowed developers to create directives
(way of marking the specification sentences) in the default API documentation.
These directives are highlighted whenever they are displayed in the eclipse environment.
Lee et al.~\cite{lee2012towards} improved upon their work by providing a formalism to the directives proposed by Dekel et al.~\cite{Dekel2009},
thus allowing tool-based verification.
However, a developer has to manually annotate such directives.
In contrast, our proposed approach both identifies the sentences pertaining to temporal constraints and infers the temporal constraints automatically.
